---
title: "Demo App"
author: "ms"
date: "`r Sys.time()`"
output: flexdashboard::flex_dashboard
runtime: shiny
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
settings <- list()
settings$packages <- list("tidyverse", "leaflet", "htmltools", "htmlwidgets",
                          "lubridate", "plotly", "shiny.semantic", "geosphere",
                          "shinydashboard")
lapply(settings$packages, library, character.only = TRUE)
options(scipen = 999999,semantic.themes = TRUE)

# read functions
source("funs.r")

# read data
# data is split and reduced in order to speed up the app
settings$ids <- "data/dictionary_ships.csv"
settings$fileName <- "data/ships_lite.csv" 
data <- list()
data$ships <- read.csv(settings$ids,
                     stringsAsFactors = F) %>% 
  janitor::clean_names()

data$raw <- read.csv(settings$fileName,
                     stringsAsFactors = F) %>%
  janitor::clean_names()

choices_start <- data$ships %>% 
  filter(ship_type == "Unspecified") %>% 
  select(shipname) %>% 
  distinct() %>% 
  pull()
```

Introduction {data-icon="fa-atlas"}
=====================================     

Column 4{data-width=100}
-------------------------------------

```{r menu}
selectizeInput("ship_type","Select type of ship:", 
            choices= sort(unique(data$ships$ship_type)), 
            selected = "Unspecified")

selectizeInput("ship_name","Select ship:", 
            choices = choices_start, 
            selected = "KONTROLER 20")

shipNames <- reactive({
 data$ships %>% 
    filter(ship_type == input$ship_type) %>% 
    as.data.frame()
})

observeEvent(
  input$ship_type,
  updateSelectizeInput(session, "ship_name",
                       label = paste("Available", input$ship_type, "ships."),
                       choices = shipNames()$shipname,
                       selected = shipNames()$shipname)
  )
```
<br>
Application created for recruitment purpose. See the task [here](https://docs.google.com/document/d/1PdTiUiGdV5n6Gb_e2Ac9pc36olXvhKfVWSbP-JxXem4/edit)

Github repository [link](https://github.com/matmusta/demo_app.git)

Have a nice day!


Column 4 
-------------------------------------


* On the left hand side you can find **menu** where you can select the vessel.

* Below there is a **summary table** which updates with each vessel selection. The table describes the trip which includes the longest sailed distance between two consecutive observations. The distance is calculated with the [Haversine method](https://en.wikipedia.org/wiki/Haversine_formula#:~:text=The%20haversine%20formula%20determines%20the,and%20angles%20of%20spherical%20triangles) that assumes a spherical earth.

* The **Map** is on the second tab.



```{r summaryTable}
renderTable({
    data <- shipFun(name = input$ship_name,
                  table = data$raw)
    
  formattable::formattable(data$stats %>% 
                             mutate(`Ship name` = input$ship_name,
                                    `Ship type` = input$ship_type) %>% 
                             select(`Ship name`, `Ship type`, everything()))
})
```


Map {data-icon="fa-atlas"}
=====================================     

```{r map}
renderLeaflet({
  data <- shipFun(name = input$ship_name,
                  table = data$raw)

  map <- data$result %>% 
    filter(datetime == max(datetime) | datetime == min(datetime))
  leaflet() %>% 
  addProviderTiles(provider = providers$Stamen.Watercolor) %>% 
  addMarkers(lng = map$lon, 
                   lat = map$lat,
                   label = lapply(map$label, HTML))
})
```


